---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(scales)
```

```{r}
recent_grads <- read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-10-16/recent-grads.csv")

majors_processed <- recent_grads %>%
  arrange(desc(Median)) %>%
  mutate(Major = str_to_title(Major),
         Major = fct_reorder(Major, Median))

```

This is one of my early data cleaning steps. 
```{r by_major_category}
by_major_category <- majors_processed %>%
  filter(!is.na(Total)) %>%
  group_by(Major_category) %>%
  summarise(Men = sum(Men),
            Women = sum(Women),
            Total = sum(Total),
            MedianSalary = sum(Median * Sample_size) / sum(Sample_size)) %>%
  mutate(ShareWomen = Women/Total) %>%
  arrange(desc(ShareWomen))
```

```{r}
theme_set(theme_light())
```




### Most common majors

What major categories (eg. engineering, psychology, business) were most common ?

```{r}
by_major_category %>%
  mutate(Major_category = fct_reorder(Major_category, Total)) %>%
  gather(Gender, Number, Men, Women) %>%
  ggplot(aes(Major_category, Number, fill = Gender)) +
  geom_col() +
  scale_y_continuous(labels = comma_format()) +
  coord_flip() +
  labs(x = "",
       y = "Total # of graduates",
       title = "What are the most common major categories?")+
  theme(legend.position = "none")
  
```

What are the most common *majors*? (Since there were 173, we're not going to show them all)
```{r}
majors_processed %>%
  mutate(Major = fct_reorder(Major, Total)) %>%
  arrange(desc(Total)) %>%
  head(20) %>%
  ggplot(aes(Major, Total, fill = Major_category)) +
  geom_col() +
  coord_flip() +
  scale_y_continuous(labels = comma_format()) +
  labs(x = "",
       y = "Total # of graduates") 
```

### What categories of majors make more money than others?
```{r}
 majors_processed %>%
  mutate(Major_category = fct_reorder(Major_category, Median)) %>%
  ggplot(aes(Major_category, Median, fill = Major_category)) +
  geom_boxplot()+
  scale_y_continuous(labels = dollar_format()) +
  expand_limits(y = 0) +
  coord_flip() +
  theme(legend.position = "none")

ggsave("boxplot.png")
```


### What are the highest earning majors?

```{r}

majors_processed %>%
  filter(Sample_size >= 100) %>%
  head(20) %>%
  ggplot(aes(Major, Median, color = Major_category)) +
  geom_point() +
  geom_errorbar(aes(ymin = P25th, ymax = P75th))+
  expand_limits(y = 0)+
  scale_y_continuous(labels = dollar_format()) +
  coord_flip() +
  labs(title = "What are the highest earning majors?",
       subtitle = "Top 20 majors with atleast 100 graduates surveyed. Bars represent the 25th to 75th percentiles.",
       x = "",
       y = "Median salary of grads")
  
```





### How does gender breakdown relate to typical earnings?

```{r}
majors_processed %>%
  arrange(desc(Total)) %>%
  head(20) %>%
  gather(Gender, Number, Men, Women) %>%
  select(Major, Gender, Number) %>%
  
```

```{r}
majors_processed %>%
  arrange(desc(Total)) %>%
  head(20) %>%
  mutate(Major = fct_reorder(Major, Total)) %>%
  gather(Gender, Number, Men, Women) %>%
  ggplot(aes(Major, Number, fill = Gender)) +
  geom_col() +
  coord_flip()
```

```{r}
majors_processed %>%
  group_by(Major_category) %>%
  summarise_at(vars(Total, Men, Women), sum, na.rm = TRUE) %>%
  mutate(ShareWomen = Women/Total) %>%
  arrange(desc(ShareWomen))
```




```{r}
library(ggrepel)

by_major_category %>%
  ggplot(aes(ShareWomen, MedianSalary))+
  geom_point()+
  geom_smooth(method = "lm")+
  geom_text_repel(aes(label = Major_category), force = .2)+
  expand_limits(y = 0)
```

```{r}
library(plotly)

g <- majors_processed %>%
    mutate(Major_category = fct_lump(Major_category, 4)) %>%
  ggplot(aes(ShareWomen, Median, color = Major_category, size = Sample_size, label = Major))+
  geom_point()+
  geom_smooth(aes(group = 1),method = "lm")+
  scale_x_continuous(labels = percent_format()) +
  scale_y_continuous(labels = dollar_format()) +
  expand_limits(y = 0)

ggplotly(g)
```

### Statistical tests
weighted linear regression
```{r}
majors_processed %>%
  select(Major, Total, ShareWomen, Sample_size, Median) %>%
  lm(Median ~ ShareWomen, data = ., weights = Sample_size) %>%
  summary()
```
Going from 0 % women to a 100% women, expected median salary would go down by 24,000$. Every % point that a field is male, the expected salary would decrease by 200-300$.

```{r}
majors_processed %>%
  select(Major, Major_category, Total, ShareWomen, Sample_size, Median) %>%
  add_count(Major_category) %>%
  filter(n >= 10) %>%
  count(Major_category)
```

```{r}

library(broom)
majors_processed %>%
  select(Major, Major_category, Total, ShareWomen, Sample_size, Median) %>%
  add_count(Major_category) %>%
  filter(n >= 10) %>%
  nest(-Major_category) %>%
  mutate(model = map(data, ~ lm(Median ~ ShareWomen, data = ., weights = Sample_size)),
         tidied = map(model, tidy)) %>%
  unnest(tidied) %>%
  filter(term == "ShareWomen") %>%
  arrange(estimate) %>%
  mutate(fdr = p.adjust(p.value, method = "fdr"))
```

p values need to be adjusted #false discovery rate

### Future works

* Examining unemploymentand fraction taking a job requiring a college degree
* Examining intrquartile ranges

```{r}
majors_processed %>%
  filter(Sample_size >= 100) %>%
  mutate(IQR = P75th - P25th) %>%
  arrange(desc(IQR))
```


```{r}
knitr::knit_exit()
```

Scrap work

```{r}
 majors_processed %>%
  group_by(Major_category) %>%
  summarise(Median = median(Median)) %>%
  mutate(Major_category = fct_reorder(Major_category, Median)) %>%
  ggplot(aes(Major_category, Median)) +
  geom_col()+
  scale_y_continuous(labels = dollar_format()) +
  coord_flip()
```


```{r}
 majors_processed %>%
  ggplot(aes(Median)) +
  geom_histogram()
```


```{r}
majors_processed %>%
  count(Major_category, wt = Total, sort = TRUE) %>%
  mutate(Major_category = fct_reorder(Major_category, n)) %>%
  ggplot(aes(Major_category, n, fill = Major_category)) +
  geom_col() +
  coord_flip() +
  labs(x = "",
       y = "Total # of graduates")+
  theme(legend.position = "none")
```


What are the lowest earning majors?
```{r}
majors_processed %>%
  filter(Sample_size >= 100) %>%
  tail(20) %>%
  ggplot(aes(Major, Median, color = Major_category)) +
  geom_point() +
  geom_errorbar(aes(ymin = P25th, ymax = P75th))+
  expand_limits(y = 0)+
  coord_flip()
```


Appendix

```{r}

majors_processed %>%
  ggplot(aes(Sample_size, Median)) +
  geom_point() +
  geom_text(aes(label = Major), check_overlap = TRUE, vjust =1, hjust = 1) +
  scale_x_log10()
```