---
title: "Untitled"
output: html_document
---

```{r}
library(tidyverse)
library(lubridate)
library(scales)
theme_set(theme_light())
```

```{r}
movie_profit_raw <- read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-10-23/movie_profit.csv")

# Data cleaning  
movie_profit <- movie_profit_raw %>%
  select(-X1) %>%
  mutate(release_date = as.Date(parse_date_time(release_date, "%m/%d/%Y"))) %>%
  filter(release_date < "2018-01-01") %>%
  arrange(desc(row_number())) %>%
  distinct(movie, release_date, .keep_all = TRUE) %>%
  mutate(distributor = fct_lump(distributor, 5)) %>%
  filter(worldwide_gross > 0) %>% 
  mutate(profit_ratio = worldwide_gross / production_budget,
        decade = 10 * floor(year(release_date) / 10))
  
```


```{r}
movie_profit %>%
  count(distributor, sort = TRUE)

movie_profit %>%
  count(movie)


movie_profit %>%
  ggplot(aes(distributor, production_budget)) +
  geom_boxplot()+
  scale_y_log10(labels = dollar_format())+
  coord_flip()
```

```{r}
movie_profit %>%
  ggplot(aes(distributor, worldwide_gross)) +
  geom_boxplot()+
  scale_y_log10(labels = dollar_format())+
  coord_flip()
```

### What genres make the most money?

```{r}
movie_profit %>%
  count(genre, sort = TRUE)
```


```{r}
movie_profit %>%
  arrange(desc(profit_ratio)) %>%
  head(20) %>%
  mutate(movie = fct_reorder(movie, profit_ratio))%>%
  ggplot(aes(movie, profit_ratio, fill = genre))+
  geom_col()+
  coord_flip()+
  scale_y_continuous(labels = function(x) paste(x, "X"))+
  labs(x = "",
       y = "Ratio of worldwide gross to production budget",
       title = "What movies have most outgrossed their budget?")
```

### What are the most common genres over time?

```{r}
movie_profit %>%
  count(decade, genre) %>%
  group_by(decade) %>%
  mutate(percent = n / sum(n)) %>%
  ggplot(aes(decade, percent, color = genre)) +
  geom_line()+
  scale_y_continuous(labels = percent_format())

```



```{r}
movie_profit %>%
  filter(!is.na(distributor)) %>%
  count(distributor, genre)%>%
  ggplot(aes(genre, n, fill = genre)) +
  geom_col(show.legend = FALSE) +
  facet_wrap( ~ distributor, scales = "free_x") +
  coord_flip()
```





```{r}
movie_profit %>% 
  mutate(genre = fct_reorder(genre, production_budget)) %>%
  ggplot(aes(genre, production_budget)) +
  geom_boxplot()+
  scale_y_log10(labels = dollar_format())+
  coord_flip()+
  facet_wrap( ~ distributor)
```
```{r}
movie_profit %>% 
  mutate(genre = fct_reorder(genre, worldwide_gross)) %>%
  filter(!is.na(distributor)) %>%
  ggplot(aes(genre, worldwide_gross)) +
  geom_boxplot()+
  scale_y_log10(labels = dollar_format())+
  coord_flip()+
  facet_wrap(~ distributor)
```
### Which genres have the biggest payoff? 
we're looking at raio of worldwide gross to production budget

```{r}
movie_profit %>%
  mutate(profit_ratio = worldwide_gross / production_budget) %>%
  arrange(profit_ratio)
```



```{r}
movie_profit %>%
  mutate(profit_ratio = worldwide_gross / production_budget) %>%
  ggplot(aes(profit_ratio))+
  geom_histogram() +
  scale_x_log10()
```

```{r}
movie_profit %>%
  mutate(profit_ratio = worldwide_gross / production_budget) %>%
  ggplot(aes(genre, profit_ratio))+
  geom_boxplot() +
  scale_y_log10()+
  coord_flip()
```


```{r}
movie_profit %>%
  group_by(genre) %>%
  summarize(median_profit_ratio = median(profit_ratio)) %>%
  arrange(desc(median_profit_ratio)) %>%
  mutate(genre = fct_reorder(genre, median_profit_ratio)) %>%
  ggplot(aes(genre, median_profit_ratio)) +
  geom_col()+
  scale_y_continuous(labels = function(x) paste(x, "X")) +
  coord_flip()
```

```{r}
movie_profit %>%
  group_by(genre, year = year(release_date)) %>%
  summarize(median_profit_ratio = median(profit_ratio),
            movies = n()) %>%
  filter(year >= "2000") %>%
  arrange(movies)
  arrange(desc(median_profit_ratio)) %>%
  mutate(genre = fct_reorder(genre, median_profit_ratio)) %>%
  ggplot(aes(genre, median_profit_ratio)) +
  geom_col()+
  scale_y_continuous(labels = function(x) paste(x, "X")) +
  coord_flip()
```





```{r}
movie_profit %>%
  group_by(genre, year = year(release_date)) %>%
  summarize(median_profit_ratio = median(profit_ratio),
            movies = n()) %>%
  ungroup() %>%
  filter(year >= 2000) %>%
  arrange(desc(median_profit_ratio)) %>%
  mutate(genre = fct_reorder(genre, median_profit_ratio)) %>%
  ggplot(aes(year, median_profit_ratio, color = genre)) +
  geom_line()+
  scale_y_continuous(labels = function(x) paste(x, "X")) 
```

Wow, horror movies have been very profitable in the last few years. What were some of those movies?

```{r}
horror_movies <- movie_profit %>%
  filter(genre == "Horror") %>%
  arrange(desc(profit_ratio)) 

horror_movies %>%
  head(10) %>%
  mutate(movie = fct_reorder(movie, profit_ratio))%>%
  ggplot(aes(movie, profit_ratio))+
  geom_col(fill = "orange")+
  coord_flip()+
  scale_y_continuous(labels = function(x) paste(x, "X"))+
  labs(x = "",
       y = "Ratio of worldwide gross to production budget",
       title = "What horror movies have most outgrossed their budget?")
```


```{r}
horror_movies %>%
  head(10) %>%
  mutate(movie = paste0(movie, " (", year(release_date), ")"),
         movie = fct_reorder(movie, profit_ratio))%>%
  ggplot(aes(movie, profit_ratio, fill = distributor))+
  geom_col()+
  coord_flip()+
  scale_y_continuous(labels = function(x) paste(x, "X"))+
  labs(x = "",
       y = "Ratio of worldwide gross to production budget",
       title = "What horror movies have most outgrossed their budget?")
```

Horror movies started being more profitable around 2013.

```{r}
horror_movies %>%
  filter(release_date >= "1990-01-01",
         profit_ratio >= .01) %>%
  ggplot(aes(release_date, profit_ratio))+
  geom_point()+
  geom_smooth(method = "lm") +
  geom_text(aes(label = movie), vjust = 1, hjust = 1, check_overlap = TRUE)+
  scale_y_log10(labels = function(x) paste0(x, "X"), breaks = c(.1,1,10, 100))
```

```{r}
movie_profit %>%
  filter(release_date >= "1990-01-01",
         profit_ratio >= .01) %>%
  ggplot(aes(release_date, profit_ratio))+
  geom_point(aes(color = genre))+
  geom_smooth(method = "lm", group = 1) +
  geom_text(aes(label = movie), vjust = 1, hjust = 1, check_overlap = TRUE)+
  scale_y_log10(labels = function(x) paste0(x, "X"), breaks = c(.1,1,10, 100))
```

```{r}
g <- movie_profit %>%
  filter(release_date >= "1990-01-01",
         profit_ratio >= .01) %>%
  ggplot(aes(release_date, profit_ratio, label = movie))+
  geom_point()+
  geom_smooth(method = "lm") +
  scale_y_log10(labels = function(x) paste0(x, "X"), breaks = c(.1,1,10, 100))+
  facet_wrap(~ genre)
library(plotly)

ggplotly(g)
```



```{r}
movie_profit %>%
  group_by(genre, distributor, decade) %>%
  summarize(median_profit_ratio = median(profit_ratio),
            movies = n()) %>%
  ungroup() %>%
  filter(decade >= 1990,
         !is.na(distributor)) %>%
  #arrange(movies)
  arrange(desc(median_profit_ratio)) %>%
  mutate(genre = fct_reorder(genre, median_profit_ratio)) %>%
  ggplot(aes(decade, median_profit_ratio, color = genre)) +
  geom_line()+
  facet_wrap(~ distributor) +
  scale_y_continuous(labels = function(x) paste(x, "X")) 
```

What are the typical budgets over time?
```{r}
movie_profit %>%
  mutate(decade = 10 * floor(year(release_date) / 10)) %>%
  count(decade) 
```

```{r}
movie_profit %>%
  mutate(decade = 10 * floor(year(release_date) / 10)) %>%
  group_by(decade) %>%
  summarise_at(vars(production_budget:worldwide_gross), median, na.rm= TRUE) %>%
  gather(metric, value, -decade) %>%
  ggplot(aes(decade, value, color = metric))+
  geom_line() +
  scale_y_continuous(labels = dollar_format())
```

```{r}
movie_profit %>%
  arrange(desc(worldwide_gross)) %>% View()
```

### Future work

domestic vs worldwide revenue
mpaa ratings
predictive model

genre release date and studio production budget script actors

